Pillar 2 - Topic Modeling

### 2019-02-18 Pillar_2_-_Topic_Modeling.Rmd

```{r}
my_control <- list(

@@

```{r}
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

```{r}
start.time <- Sys.time()

@@

save(result_descrition,
     file = "Output/LDA_ntopics_description.RDATA")

@@

```{r}
start.time <- Sys.time()

@@

```{r, eval = F}
start.time <- Sys.time()

@@

result_descrition %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

>>>>

```{r controls}
my_control <- list(

@@

```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

```{r description topics, cache = TRUE}
start.time <- Sys.time()

@@

save(result_description,
     file = "Output/LDA_ntopics_description.RDATA")

@@

```{r overview topics, cache = TRUE}
start.time <- Sys.time()

@@

```{r manual topics, cache = TRUE}
start.time <- Sys.time()

@@

result_description %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot
